\documentclass[draft, 12pt]{book}

\title{Everyone Pays Taxes!}
\author{Iris Fung, Paul Hager}

\begin{document}

\frontmatter

\maketitle

\mainmatter

Once upon a time, there was a group of families.
%Zoo

The flock of goats
% Would be cute a goat being frightened in the background

The herd of antelopes

The {embarrassment, cupboard, bamboo} of pandas
% Cupboard of pandas seems funny

The children of these families were bored with no place to spend time together except one others' houses.
% Lost children

Whenever the kids played inside they made their homes dirty :sadface:

One day, Antelope said "Let's build a sandbox!" The others eagerly agreed. 

When the three visited the hardware store, the price of a sandbox was too expensive!
% Price tag: \$1 quadrillion

Each of the children asked their families if they could buy the sandbox for them, 
% Rich families may rip out the pages of the rest of the book except appendix 0

They all decided they would save money together to purchase the 

They made a special place for the money they saved to go.
% Chest with Calvin and Hobbes-esque "Sandbox Fund"

Goat mowed each of their neighbor's grass, and for each lawn they contributed a portion to the sandbox.

Antelope bought an expensive hat their horns and took some of the money and put it into the {chest, fund}

Panda owned a tree house.
A {barrel, troop} of monkeys [rented this treehouse and therefore] paid Panda every month to live in it.
Panda took some of this money and saved it for the sandbox.

Eventually they had enough money for the sandbox and happily enjoyed their new shared playground

Goat thought it would be fun to have toys in the sandbox for everyone to use.
Buying toys would require saving more money, extra money Antelope and Panda did not want to save.

Goat saved money by them self and bought the toys.
% Shovel, bucket

When other animals wanted to use the toys they could {trade, rent} for them.

{Cat came and visited the sandbox and mistook it for a bathroom.,
Over time the sandbox got dirty and playing was less fun.}

They knew they would have to save money to pay for a weekly sandbox cleaning.
But they did not know how exactly.

They could raise money like the first time by saving when they worked or bought {nice things, luxuries}.
% Thought bubble pictures of the above illustrations
Or they could save a little money every time they went used the sandbox.

The group decided to do both they saved less than before and when they or any other animal came and visited the sandbox{;, ,} they paid an entry fee.
% Toll booth

[They lived happily enjoying their shared sandbox!]
% Fun group picture

\pagebreak

\appendix
\section{Appendix}
The families paid for the sandbox, the children enjoyed their new shared playground, and lived happily every after.

\backmatter
\chapter{Bibliography}
Significant credit if not direct royalties :winky: needs to be given to The Children's Illustrated Guide to Kubernetes for inspiration.
Credit also goes to Taro Gomi's Everyone Poops.

\end{document}
